\LARGE \bf Reactive Path Planning with Pedestrains for Autonomous Driving

### 2016-01-20 paper2.tex
remove gomentum images

\usepackage[pdftex]{graphicx}
\usepackage{algpseudocode}
\usepackage[noadjust]{cite}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/zenrin.png}
  \caption{High resolution map. Red color is at road edges. Green color shows lane center-lines}
  \label{fig:map}
\end{figure}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/GoMentumSatelliteSmall.png}
  \caption{Gomentum map top view}
  \label{fig:gomentum}
\end{figure}

We assume that we have access to Path Planner. This can be for example a service similar to
Google Maps except that it provides lane level maps. We also assume that we have a High
Resolution digital map such as one shown in Figure \ref{fig:map} [corresponding to 
Figure \ref{fig:gomentum}] with Lane centers, Stop 
signs, crosswalk geometry, and Turning curves at intersections. The starting position the 
car is determined via high grade GPS. The destination is manually input into the system.
Using the path planner, we obtain a path along lane centers from start to the destination.
This plan is output as waypoints, with the waypoints corresponding to stop signs marked.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/ped-detection-screenshot.png}
  \caption{Showing detected pedestrian by the computer vision system}
  \label{fig:ped}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/RSTOP_NORMAL.png}
  \caption{Normal mode}
  \label{fig:react1}
\end{figure}
\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RSTOP.png}
  \caption{Stopping for the pedestrian mode}
  \label{fig:react2}
\end{figure}
\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RESUME.png}
  \caption{Resuming after stop sign}
  \label{fig:react3}
\end{figure}

>>>>

\usepackage[pdftex]{graphicx}
\usepackage{algpseudocode}
\usepackage{subfigure}
\usepackage[noadjust]{cite}

@@

We assume that we have access to Path Planner. This can be for example a service similar to
Google Maps except that it provides lane level maps. We also assume that we have a High
Resolution digital map with Lane centers, Stop signs, crosswalk geometry, and Turning 
curves at intersections. The starting position the 
car is determined via high grade GPS. The destination is manually input into the system.
Using the path planner, we obtain a path along lane centers from start to the destination.
This plan is output as waypoints, with the waypoints corresponding to stop signs marked.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/ped2.png}
  \caption{Showing detected pedestrian by the computer vision system}
  \label{fig:ped}
\end{figure}

@@

\begin{figure}[thpb]
\centering
  \subfigure[Normal mode]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_NORMAL.png}}
\\
  \subfigure[Stopping for the pedestrian]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RSTOP.png}}
\\
  \subfigure[Resuming after stop sign]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RESUME.png}}
  \caption{Reactive behavior to pedestrain}
  \label{fig:react}
\end{figure}
